---
title: "ggplot2_exercise"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here: Shayla Wu



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
ideology <- recode(cces$ideo5,`1`="Very liberal",`2`="Liberal",`3`="Moderate",`4`="Conservative",`5`="Very conservative")

cces %>% add_column(ideology) %>%
  ggplot(aes(x=ideology,fill=ideology)) +
  geom_bar() +
  labs(x="Ideology",y="Count",title="Respondent Ideology") +
  guides(fill="none")
```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
religimp <- recode(cces$pew_religimp,`1`="Very imp.",`2`="Somewhat imp.",`3`="Not too imp.",`4`="Not imp.")

cces %>% add_column(ideology) %>%
  add_column(religimp) %>%
  rename(Ideology=ideology) %>%
  ggplot(aes(x=religimp,fill=Ideology)) +
  geom_bar() +
  labs(x="Importance of Religion",y="Count",title="Importance of Religion by Ideology") 
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
semester <- c(1:6)
student <- c("Amanda","Betty","Carol")
dat3 <- expand.grid(Semester=semester,Student=student)
dat3$Grade <- runif(18,80,100)

ggplot(dat3,aes(x=Semester,y=Grade,group=Student,color=Student)) +
  geom_line() +
  facet_wrap(~Student) +
  labs(title = "Student Grades by Semester") +
  theme(legend.position="none")
```
