---
title: "graphical_elements_exercise"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(viridis)
library(hrbrthemes)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Shayla Wu

## Exercise 1

#### Explain what you are visualizing here:

1. Besides those full-vote MC, visualize vote-percent each MC won.
2. Group by whether the MC is Democrat and whether was state legislator.
3. Use **theme_ipsum**

#### Put your figure here:

```{r exercise1,echo=FALSE,out.width = '90%',fig.asp=1}
democrat <- recode(cel$dem,`1`="Democrat",`0`="Not Democrat")
stateleg <- recode(cel$state_leg,`1`="Was State Legislator",`0`="Was Not State Legislator")
cel1 <- cel %>% mutate(vote_level = case_when(votepct_sq<=2500~"Low",
                                      votepct_sq<=7500~"Mid",
                                      seniority<=10000~"High"))

cel1 %>% add_column(democrat,stateleg) %>% filter(votepct_sq!=10000) %>% 
  ggplot(aes(thomas_num,votepct,colour=votepct)) +
  geom_point(alpha=.4,shape = 16,size=1.5) + 
  facet_wrap(~democrat+stateleg) +
  geom_rug(sides="l",alpha=0.05,size=0.7) + 
  theme_ipsum() +
  labs(x="Member of Congress",
       y="Vote Percent",
       title="Poll of Congress Members") +
  theme(axis.text.x=element_blank(),
        legend.position="none") +
  geom_hline(yintercept = 90,colour="red",alpha=.5)

```

## Exercise 2

#### Explain what you are visualizing here:

1. Devide MC into 4 groups based on vote percents.
2. Summarise the distribution of vote percent for each group by boxplot.
3. Compare horizontally between majority MC and minority MC. 
4. Use **theme_stata**

#### Put your figure here:

```{r exercise2,echo=FALSE}
cel2 <- cel %>% mutate(Seniority = case_when(seniority<=2~"Very Low",
                                             seniority<=4~"Low",
                                             seniority<=7~"High",
                                             seniority<=30~"Very High"))
Majority <- recode(cel$majority,`0`="Minority",`1`="Majority")

cel2 %>%
  add_column(Majority) %>%
  ggplot(aes(x=Seniority, y = votepct,fill=Majority)) +
  geom_boxplot(outlier.size = 1,
               outlier.colour="coral2") +
  theme_stata() +
  labs(x="Level of Seniority",y="Vote Percent",
       title="Vote Percent by Level of Seniority")
  
```

## Exercise 3

#### Explain what you are visualizing here:

1. Visualize respondents' ideology by bar plot.
2. Visualize gender difference by fill color and overlap bars.

#### Put your figure here:

```{r exercise3,echo=FALSE}
ideology <- recode(cces$ideo5,`1`="Very liberal",`2`="Liberal",`3`="Moderate",`4`="Conservative",`5`="Very conservative")
Gender <- recode_factor(cces$gender, '1' = 'Male', '2' = 'Female')

cces %>% 
  # add_column(ideology) %>%
  # ggplot(aes(x=ideology,fill=ideology)) +
  add_column(Gender,ideology) %>% 
  ggplot(aes(x=ideology,fill=Gender)) +
  geom_bar(position = "identity",
           alpha=0.5) +
  labs(x="Ideology",y="Count",title="Respondent Ideology")
```

## Exercise 4

#### Explain what you are visualizing here:

1. Visualize bill introduction by states over years (started from 1981)
2. Compare bill introduction by regions
3. Use **theme_ipsum**

#### Put your figure here:

```{r exercise4,echo=FALSE,message = FALSE,out.width = '100%'}
st_region_index <- c()
for (st in cel$st_name){st_region_index <- c(st_region_index,which(state.abb==st))}
st_region <- state.region[c(st_region_index)]
cel4 <- cel %>%
  select(st_name,year,all_bills) %>%
  mutate(Region=st_region,region=st_region) 

dat4 <- cel4 %>%
  group_by(st_name,year,region) %>%
  summarise(st_all_bills=sum(all_bills))

dat4 <- dat4 %>% 
  mutate(Region=region) %>%
  filter(year>1980)

add_label <- data.frame(year=c(2002,2002),st_all_bills=c(800,650),region=c("West","Northeast"))

dat4 %>% 
  ggplot(aes(x=year,y=st_all_bills)) + 
  geom_line(data=dat4 %>% dplyr::select(-region),
            aes(group=st_name), color="grey", size=0.5, alpha=0.5) +
  geom_line(aes(group=st_name,colour=region), size=0.7,alpha=0.7) +
  scale_color_viridis(discrete = TRUE) +
  theme_ipsum() +
  theme(
    # legend.position="none",
    plot.title = element_text(size=14),
    panel.grid = element_blank()
  ) +
  labs(x="Year",y="Bill Introdution by State") +
  ggtitle("A Spaghetti Chart of Bill Introduction") +
  facet_wrap(~region) +
  geom_label(data=add_label,label=c("NY","CA"),fill=c("darkgoldenrod1","darkorchid4"),colour=c("black","white"))

```
